---
title: "Untitled"
author: "AI Casas"
date: "5/2/2020"
output: pdf_document
---

```{r}
getwd()
setwd("/Users/ppm/Desktop/R Course/First/exdata")
all <- readRDS("summarySCC_PM25.rds")
all
subs <- head(all)
subs
```

Playing around
```{r}
boxplot(all$Emissions, color = "blue")
```
Playing around
```{r}
hist(all$Emissions, col = "blue", breaks = 100)
rug(all$Emissions)
```

```{r}
iris
iris[iris$Species == "setosa", ]
```

Plot an histogram and set a vertical line
```{r}
pr <- split(iris, iris$Species)
hist(iris$Sepal.Length)
abline(v = 7, col = "magenta")
```

Plot a barplot
```{r}
barplot(iris$Sepal.Length)
```

Plot different colors based on a variable
```{r}
with(iris, plot(iris$Sepal.Length, Petal.Length, col = iris$Species))
```

Set the color you want in your scatterplot
```{r}
with(cars, plot(speed, dist, col = "red"))
```

Playing around with lattice
```{r}
library(lattice)
state <- data.frame(state.x77, region = state.region)
xyplot(Life.Exp ~ Income | region, data = state, layout = c(1, 4))
```

```{r}
data(mpg)
mpg
```

```{r}
library(datasets)
hist(airquality$Ozone)
```
Plot a legend, different colors based on variables, plot a title
```{r}
with(airquality, plot(Wind, Ozone))
title(main = "Ozone and Wind in NY")
with(subset(airquality, Month == 5), points(Wind, Ozone, col = "blue"))
with(subset(airquality, Month != 5), points(Wind, Ozone, col = "red"))
legend("topright", pch = 1, col = c("blue", "red"), legend = c("May", "Other months"))
```

How to set a linear model and plot the line associated with it. This line can have different thickness and color.
How to change the symbols for the plot, i.e. circles, triangules, square, etc..
```{r}

with(airquality, plot(Wind, Ozone, main = "Ozone and Wind in NY", pch = 4))
abline(lm(Ozone ~ Wind, airquality), lwd = 2, col = "red")
par(mar = c(3,3,3, 3))

```

If you dont want to execute/include the data since the beggining
```{r}
with(airquality, plot(Wind, Ozone, main = "Ozone and Wind in NY", pch = 4, type = "n"))
```

```{r}
pdf(file = "myplot_example.pdf")
with(airquality, plot(Wind, Ozone, main = "Ozone and Wind in NY", pch = 4))
abline(lm(Ozone ~ Wind, airquality), lwd = 2, col = "red")
dev.off()
```

```{r}
dev.cur()
```

