---
title: "Loop functions"
author: "AI Casas"
date: "4/22/2020"
output: pdf_document
---

Loop functions:lappy

```{r}
x <- list(a = 1:5, b = rnorm(10))
x
lapply(x, mean)
```

```{r}
?runif()
```

```{r}
g <- list(a = matrix(1:4, 2, 2), b = matrix(1:6, 3, 2))
g
lapply(g, function(elt) elt[,1])
```

Loop Functions: apply

```{r}
r <- matrix(rnorm(200), 20, 10)
apply(r, 1, quantile, probs = c(0.25, 0.75))
```

Loop Functions: mapply

```{r}
mapply(rep, 1:4, 4:1)
```
La mapply no la entiendo


```{r}
e <- rep(1:4)
e

```


Loop function: tapply 
```{r}
x <- c(rnorm(10), runif(10), rnorm(10, 1))
x
f <- gl(3, 10)
f
```

```{r}
tapply(x, f, mean)
?gl
gl(3, 10)
```

Impartante tener en cuenta que a la tapply le tienens que decir como formar los subsets del vector principal que le estas dando. Es decir, si el vector x tiene 2 "trozos" o niveles, le tienes que incluir un INDEX (en este caso "f") de la misma longitud que le diga que hay 3 grupos de 10 cada uno (en este caso)

Split: It is not a loop function

```{r}
x <- c(rnorm(10), runif(10), rnorm(10, 1))
x
f <- gl(3, 10)
f
split(x, f)
```

You can use the split together with the lapplay or sapplay
```{r}
lapply(split(x,f), mean)
```

However you can do exactly the same thing by using tapply
```{r}
tapply(x, f, mean)
```

Same results, then

How to use the split function in data frames
```{r}
getwd()
setwd("/Users/ppm/Desktop/R Course/First/")
getwd()
read.csv("hw1_data.csv")
```

You can split the df based on months and then apply a function to each section
```{r}
df <- read.csv("hw1_data.csv")
df2 <- split(df, df$Month)
lapply(df2, function(df2) colMeans(df2[c("Solar.R", "Wind")]))
```

Instead of the lapply you can implement sapply if you dont want a list but a matrix where the "5-9" numbers represent the month
```{r}
sapply(df2, function(df2) colMeans(df2[c("Solar.R", "Wind")], na.rm = TRUE))
```

